---
title: "HEUS-Paper-Stage1"
author: "John Cornwell"
date: "February 6, 2017"
output: pdf_document
---

## Import and fire packages.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(RMySQL)
library(dplyr)
library(tidyr)
library(knitr)
library(reshape2)
library(plyr)
library(DT)
library(foreign)
library(qdap)
install.packages("weights")
library(weights)
# useful paste function

paste5 <- function(..., sep = " ", collapse = NULL, na.rm = F) {
  if (na.rm == F)
    paste(..., sep = sep, collapse = collapse)
  else
    if (na.rm == T) {
      paste.na <- function(x, sep) {
        x <- gsub("^\\s+|\\s+$", "", x)
        ret <- paste(na.omit(x), collapse = sep)
        is.na(ret) <- ret == ""
        return(ret)
      }
      df <- data.frame(..., stringsAsFactors = F)
      ret <- apply(df, 1, FUN = function(x) paste.na(x, sep))

      if (is.null(collapse))
        ret
      else {
        paste.na(ret, sep = collapse)
      }
    }
}

```

## Data Cleaning
# First step is to import and clean lighting data.
```{r }
### -- Lighting cleaning -----

# Import Lighting CSV files using cleaned CSV files on Augur.

folder <- '/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/5 - Final Cleaning with QC and CEC/'
SFlighting <- read.csv(paste(folder, 'SFlighting_clean_qc.csv', sep = "/"), stringsAsFactors = F)
SFlightingLamp <- read.csv(paste(folder,'SFlightingLamp_clean_qc.csv', sep = "/"), stringsAsFactors = F)
SFextlighting <- read.csv(paste(folder,'SFextlighting_clean_qc.csv', sep = "/"), stringsAsFactors = F)
SFextlightingLamp <- read.csv(paste(folder, 'SFextlightingLamp_clean_qc.csv', sep="/"), stringsAsFactors = F)

# Drop QC flags and notes
SFlighting <- select(SFlighting, -(QC19_NoLighting:QC19_Room_its..room...))
SFlightingLamp <- select(SFlightingLamp, -(QC19_NoLighting:QC25_room_fixture_it.y), -(QC21:QC_Lighting))
SFextlighting <- select(SFextlighting, -(QC19_NoLighting:QC19_Room_its..room...), -Exterior)
SFextlightingLamp <- select(SFextlightingLamp, -(QC19_NoLighting:QC19_Room_its..room...), -(QC21:QC_Lighting))

SFlighting <- select(SFlighting, -(X))
SFlightingLamp <- select(SFlightingLamp, -(X))
SFextlighting <- select(SFextlighting, -(X))
SFextlightingLamp <- select(SFextlightingLamp, -(X))

# Join interior and exterior lighting tables
All_Lighting_lamps <- rbind(SFlightingLamp, SFextlightingLamp)

```

# Add variables for effieicnt vs inefficient lighting to lamp table. Inefficient = Incandescent and Linear F and Unknown. Efficient = CFL AND LED.
```{r }

# Create flag for efficient lamp.
All_Lighting_lamps$EfficientLamp <-NA
for (i in 1:length(All_Lighting_lamps$siteid)){
  if ((All_Lighting_lamps$LightingLampCategory[i]=="Halogen") | (All_Lighting_lamps$LightingLampCategory[i]=="Incandescent") | (All_Lighting_lamps$LightingLampCategory[i]=="Linear Fluorescent")) {
      All_Lighting_lamps$EfficientLamp[i]<-"NE"
  }
}

for (i in 1:length(All_Lighting_lamps$siteid)){
  if ((All_Lighting_lamps$LightingLampCategory[i]=="Compact Fluorescent") | (All_Lighting_lamps$LightingLampCategory[i]=="LED")){
      All_Lighting_lamps$EfficientLamp[i]<-"E"
  }
}
  
## Create dataframe with lamp sums.
All_Lighting_lamps$LightingLampsPerFixture <- as.numeric(All_Lighting_lamps$LightingLampsPerFixture)
Summary_Lighting_Eff <- All_Lighting_lamps %>% 
  group_by(siteid, EfficientLamp)
Summary_Lighting_Eff <- summarise_each(Summary_Lighting_Eff, funs(sum),LightingLampsPerFixture)
Summary_Lighting_Eff <- spread(Summary_Lighting_Eff, EfficientLamp, LightingLampsPerFixture)

#create variable for percent of lamps that are efficient
Summary_Lighting_Eff <- ungroup(Summary_Lighting_Eff)
Summary_Lighting_Eff$E[is.na(Summary_Lighting_Eff$E)] <- 0
Summary_Lighting_Eff$NE[is.na(Summary_Lighting_Eff$NE)] <- 0
Summary_Lighting_Eff <- mutate(Summary_Lighting_Eff, perc_eff = E/(E+NE))

# assign homes to deciles
Summary_Lighting_Eff <- mutate(Summary_Lighting_Eff, Decile = ntile(perc_eff, 10))

Summary_Lighting_Eff %>% group_by(Decile) %>% summarise_each(funs(min,max),perc_eff)

# append to home data
folder <- '/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/3 - Initial Cleaning and QC/'
HomeData1<- read.csv(paste(folder, 'SFMaster_housegeometry_clean.csv', sep = "/"), stringsAsFactors = F)
HomeData2 <- read.csv(paste('/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/2 - Restructured Tables/SF_ri_demog.csv', sep = "/"), stringsAsFactors = F)
HomeData3 <- read.csv(paste('/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/2 - Restructured Tables/SF_ri_custdat.csv', sep = "/"), stringsAsFactors = F)

HomeData <- left_join(HomeData1, HomeData2, by = "siteid")
HomeData <- left_join(HomeData, HomeData3, by = "siteid")

rm (HomeData1, HomeData2, HomeData3)
Lighting_Eff_HomeData <- left_join(Summary_Lighting_Eff, HomeData, by = "siteid")

## append weights

Weights <- read.csv(paste('/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/0 - Weights/FinalWeights_BySiteID_072816.csv', sep = "/"), stringsAsFactors = F)
Lighting_Eff_HomeData <- left_join(Lighting_Eff_HomeData, Weights, by = "siteid")

wtd.median(Lighting_Eff_HomeData$perc_eff, weights=Lighting_Eff_HomeData$weight_strata_prop, 
             normwt=FALSE, na.rm=TRUE)

Summary_Lighting_Eff %>% group_by(Decile) %>% summarise_each(funs(min,max),perc_eff)

```


## Data Analysis
```{r cars}
summary(Lighting_Eff_HomeData)
table(Lighting_Eff_HomeData$Decile)
wtd.hist(Lighting_Eff_HomeData$perc_eff, breaks = 50, xlab = "Percent Efficient Lighting", border = "blue", col = "green", weight = Lighting_Eff_HomeData$weight_strata_prop)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
