---
title: "HEUS-Paper-Stage1"
author: "John Cornwell"
date: "February 6, 2017"
output: pdf_document
---

## Import and fire packages.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(RMySQL)
library(dplyr)
library(tidyr)
library(knitr)
library(reshape2)
library(plyr)
library(DT)
library(foreign)
library(qdap)
install.packages("weights")
library(weights)
# useful paste function

paste5 <- function(..., sep = " ", collapse = NULL, na.rm = F) {
  if (na.rm == F)
    paste(..., sep = sep, collapse = collapse)
  else
    if (na.rm == T) {
      paste.na <- function(x, sep) {
        x <- gsub("^\\s+|\\s+$", "", x)
        ret <- paste(na.omit(x), collapse = sep)
        is.na(ret) <- ret == ""
        return(ret)
      }
      df <- data.frame(..., stringsAsFactors = F)
      ret <- apply(df, 1, FUN = function(x) paste.na(x, sep))

      if (is.null(collapse))
        ret
      else {
        paste.na(ret, sep = collapse)
      }
    }
}

save.xlsx <- function (file, ...)
  {
      require(xlsx, quietly = TRUE)
      objects <- list(...)
      fargs <- as.list(match.call(expand.dots = TRUE))
      objnames <- as.character(fargs)[-c(1, 2)]
      nobjects <- length(objects)
      for (i in 1:nobjects) {
          if (i == 1)
              write.xlsx(objects[[i]], file, sheetName = objnames[i])
          else write.xlsx(objects[[i]], file, sheetName = objnames[i],
              append = TRUE)
      }
      print(paste("Workbook", file, "has", nobjects, "worksheets."))
}
x<- as.list(incdtab,
eddtab,
vintdtab,
htdtab,
sqftdtab,
BNBdtab,
CZdtab,
cntydtab)
save.xlsx("myworkbook.xlsx", x)
[1] "Workbook myworkbook.xlsx has 4 worksheets."
```

## Data Cleaning
# First step is to import and clean lighting data.
```{r }
### -- Lighting cleaning -----

# Import Lighting CSV files using cleaned CSV files on Augur.

folder <- '/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/5 - Final Cleaning with QC and CEC/'
SFlighting <- read.csv(paste(folder, 'SFlighting_clean_qc.csv', sep = "/"), stringsAsFactors = F)
SFlightingLamp <- read.csv(paste(folder,'SFlightingLamp_clean_qc.csv', sep = "/"), stringsAsFactors = F)
SFextlighting <- read.csv(paste(folder,'SFextlighting_clean_qc.csv', sep = "/"), stringsAsFactors = F)
SFextlightingLamp <- read.csv(paste(folder, 'SFextlightingLamp_clean_qc.csv', sep="/"), stringsAsFactors = F)

# Drop QC flags and notes
SFlighting <- select(SFlighting, -(QC19_NoLighting:QC19_Room_its..room...))
SFlightingLamp <- select(SFlightingLamp, -(QC19_NoLighting:QC25_room_fixture_it.y), -(QC21:QC_Lighting))
SFextlighting <- select(SFextlighting, -(QC19_NoLighting:QC19_Room_its..room...), -Exterior)
SFextlightingLamp <- select(SFextlightingLamp, -(QC19_NoLighting:QC19_Room_its..room...), -(QC21:QC_Lighting))

SFlighting <- select(SFlighting, -(X))
SFlightingLamp <- select(SFlightingLamp, -(X))
SFextlighting <- select(SFextlighting, -(X))
SFextlightingLamp <- select(SFextlightingLamp, -(X))

# Join interior and exterior lighting tables
All_Lighting_lamps <- rbind(SFlightingLamp, SFextlightingLamp)

```

# Add variables for effieicnt vs inefficient lighting to lamp table. Inefficient = Incandescent and Linear F and Unknown. Efficient = CFL AND LED.
```{r }

# Create flag for efficient lamp.
All_Lighting_lamps$EfficientLamp <-NA
for (i in 1:length(All_Lighting_lamps$siteid)){
  if ((All_Lighting_lamps$LightingLampCategory[i]=="Halogen") | (All_Lighting_lamps$LightingLampCategory[i]=="Incandescent") | (All_Lighting_lamps$LightingLampCategory[i]=="Linear Fluorescent")) {
      All_Lighting_lamps$EfficientLamp[i]<-"NE"
  }
}

for (i in 1:length(All_Lighting_lamps$siteid)){
  if ((All_Lighting_lamps$LightingLampCategory[i]=="Compact Fluorescent") | (All_Lighting_lamps$LightingLampCategory[i]=="LED")){
      All_Lighting_lamps$EfficientLamp[i]<-"E"
  }
}
  
## Create dataframe with lamp sums.
All_Lighting_lamps$LightingLampsPerFixture <- as.numeric(All_Lighting_lamps$LightingLampsPerFixture)
Summary_Lighting_Eff <- All_Lighting_lamps %>% 
  group_by(siteid, EfficientLamp)
Summary_Lighting_Eff <- summarise_each(Summary_Lighting_Eff, funs(sum),LightingLampsPerFixture)
Summary_Lighting_Eff <- spread(Summary_Lighting_Eff, EfficientLamp, LightingLampsPerFixture)

#create variable for percent of lamps that are efficient
Summary_Lighting_Eff <- ungroup(Summary_Lighting_Eff)
Summary_Lighting_Eff$E[is.na(Summary_Lighting_Eff$E)] <- 0
Summary_Lighting_Eff$NE[is.na(Summary_Lighting_Eff$NE)] <- 0
Summary_Lighting_Eff <- mutate(Summary_Lighting_Eff, perc_eff = E/(E+NE))

# assign homes to deciles
Summary_Lighting_Eff <- mutate(Summary_Lighting_Eff, Decile = ntile(perc_eff, 10))

Summary_Lighting_Eff %>% group_by(Decile) %>% summarise_each(funs(min,max),perc_eff)

# append to home data
folder <- '/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/3 - Initial Cleaning and QC/'
HomeData1<- read.csv(paste(folder, 'SFMaster_housegeometry_clean.csv', sep = "/"), stringsAsFactors = F)
HomeData2 <- read.csv(paste('/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/2 - Restructured Tables/SF_ri_demog.csv', sep = "/"), stringsAsFactors = F)
HomeData3 <- read.csv(paste('/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/2 - Restructured Tables/SF_ri_custdat.csv', sep = "/"), stringsAsFactors = F)

HomeData <- left_join(HomeData1, HomeData2, by = "siteid")
HomeData <- left_join(HomeData, HomeData3, by = "siteid")

rm (HomeData1, HomeData2, HomeData3)
Lighting_Eff_HomeData <- left_join(Summary_Lighting_Eff, HomeData, by = "siteid")

## append weights

Weights <- read.csv(paste('/Volumes/Projects/401013 - PG&E RBSA/Data/Data - MASTER/0 - Weights/FinalWeights_BySiteID_072816.csv', sep = "/"), stringsAsFactors = F)
Lighting_Eff_HomeData <- left_join(Lighting_Eff_HomeData, Weights, by = "siteid")

wtd.median(Lighting_Eff_HomeData$perc_eff, weights=Lighting_Eff_HomeData$weight_strata_prop, 
             normwt=FALSE, na.rm=TRUE)

Summary_Lighting_Eff %>% group_by(Decile) %>% summarise_each(funs(min,max),perc_eff)

Lighting_Eff_HomeData$yrbins <- cut(Lighting_Eff_HomeData$ResInt_YearBuilt, breaks=c(0,1920,1940,1960,1980,2000,2020), labels=c("<1920","1920-1940","1940-1960","1960-1980","1980-2000",">2000"))

Lighting_Eff_HomeData$sqftbins <- cut(Lighting_Eff_HomeData$SummarySketchSqFt_Calculated, breaks=c(0,500,1000,1500,2000,2500,3000,4000,25000), labels=c("<<500","500-1000","1000-1500","1500-2000","2000-2500","2500-3000","3000-4000",">4000"))

```


## Data Analysis - 
<!-- Bin appliances by efficiency level (maybe just efficient vs inefficient) -->

<!-- -	Demographics (income, education level) -->
<!-- -	Housing characteristics (vintage, SF vs MF, presence of solar, Zillow estimate for home price?) -->
<!-- -	Geographic (urban vs rural, bay area vs non-bay area, climate zones, county). -->
<!-- -	Certain equipment as keystone species? If you have an EE refrigerator, maybe you have only EE stuff? -->

<!-- Next steps -->
<!-- 1)	Incandescent % and # bin graph of weighted # homes (end of Monday) -->
<!-- 2)	Cross tabs by demographics -->
<!-- 3)	Cross tabs by housing characteristics -->

```{r }
summary(Lighting_Eff_HomeData)
table(Lighting_Eff_HomeData$Decile)
wtd.hist(Lighting_Eff_HomeData$perc_eff, breaks = 50, xlab = "Percent Efficient Lighting", border = "blue", col = "green", weight = Lighting_Eff_HomeData$weight_strata_prop)

incdtab <- table(Lighting_Eff_HomeData$ResInt_Income, Lighting_Eff_HomeData$Decile)
eddtab <- table(Lighting_Eff_HomeData$ResInt_Education, Lighting_Eff_HomeData$Decile)
vintdtab <- table(Lighting_Eff_HomeData$yrbins, Lighting_Eff_HomeData$Decile)
htdtab <- table(Lighting_Eff_HomeData$SFBuildingType, Lighting_Eff_HomeData$Decile)
sqftdtab <- table(Lighting_Eff_HomeData$sqftbins, Lighting_Eff_HomeData$Decile)
BNBdtab <- table(Lighting_Eff_HomeData$Bay, Lighting_Eff_HomeData$Decile)
CZdtab <- table(Lighting_Eff_HomeData$DOEZone, Lighting_Eff_HomeData$Decile)
cntydtab <- table(Lighting_Eff_HomeData$county, Lighting_Eff_HomeData$Decile)

incdtab
eddtab
vintdtab
htdtab
sqftdtab
BNBdtab
CZdtab
cntydtab

incgroupmn <- Lighting_Eff_HomeData %>% group_by(ResInt_Income) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
edgroupmn <- Lighting_Eff_HomeData %>% group_by(ResInt_Education) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
vintgroupmn <- Lighting_Eff_HomeData %>% group_by(yrbins) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
htgroupmn <- Lighting_Eff_HomeData %>% group_by(SFBuildingType) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
sqftgroupmn <- Lighting_Eff_HomeData %>% group_by(sqftbins) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
BNBgroupmn <- Lighting_Eff_HomeData %>% group_by(Bay) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
CZgroupmn <- Lighting_Eff_HomeData %>% group_by(DOEZone) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)
cntygroupmn <- Lighting_Eff_HomeData %>% group_by(county) %>% summarise_each(funs(mean(perc_eff,na.rm=T),n()),perc_eff)


incgroupmn
edgroupmn
vintgroupmn
htgroupmn
sqftgroupmn
BNBgroupmn 
CZgroupmn
cntygroupmn
```


## Including Plots

You can also embed plots, for example:

```{r }
ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$ResInt_Income, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$ResInt_Income)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$ResInt_Education, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$ResInt_Education)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$yrbins, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$yrbins)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$SFBuildingType, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$SFBuildingType)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$sqftbins, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$sqftbins)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$Bay, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$Bay)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$DOEZone, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$DOEZone)) + geom_boxplot()

ggplot(Lighting_Eff_HomeData, aes(x=Lighting_Eff_HomeData$county, y=Lighting_Eff_HomeData$perc_eff, fill=Lighting_Eff_HomeData$county)) + geom_boxplot()

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
